Turbulence in compact to giant H~II regions

### 2023-04-27 strucfunc_paper.tex
Further changes to the intro to Appendix A

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \NEW{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \NEW{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

@@

The 3-dimensional 2nd-order structure function slope is related to the power law index as \(m\DDD = n - 3\), but the slope, \(m\), of the 2-dimensional velocity
structure function depends not only on velocity power law index, but also on the magnitude and power law index of the emissivity fluctuations via the quantity
\(\delta\kappa\), with the relation being \(m = n - 2 + \delta\kappa\)
(see section \ref{sec:constancy-power-law}).
\citet{Brunt:2004a} found that \(\delta\kappa\) is a function of the Mach number for
hydrodynamic turbulent box simulations, but we are unaware of any analytic prescription that would allow us to calculate \(\delta\kappa\) for
the fractional Brownian motion models that we use here. 
We therefore adopt an empirical approach by varying \(n\) until the
resultant structure function slope matches a particular value in the
range \(m = 0.8 \to 1.2\)
that encompasses our observational results. 
At each step, we estimate \(m\) by fitting our idealized model structure function
(equation~\eqref{eq:model-strucfunc-ideal}, without the seeing and noise terms)
to the structure function of the simulated velocity map.
In the case of a uniform emissivity field (\(\shortsig{E} = 0\)),
we find \(\delta\kappa \approx 0\),
which is maximal projection smoothing, exactly as expected for a case that
mimics incompressible turbulence.
As the amplitude of the emissivity fluctuations increase,
we find that \(\delta\kappa\) becomes increasingly negative,
with \(\delta\kappa \approx -0.3\) for \(\shortsig{E} = 1\) (the case that we present here)
and \(\delta\kappa \approx -0.55\) for \(\shortsig{E} = 2\).
This is qualitatively consistent with the results in
Figure~12a of \citet{Brunt:2004a}, although a quantitative
comparison is hard to make, since they are not holding \(m\) constant
in the way we do here. 
\stopNEW

>>>>

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \NEW{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \NEW{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n\DDD}\),
and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

@@

\newcommand\DD{\ensuremath{_{\mathrm{2D}}}}
The 3-dimensional 2nd-order structure function slope is related to the power law index as \(m\DDD = n\DDD - 3\), while the equivalent relation in two dimensions is \(m\DD = n\DD - 2\) for separations smaller than the line-of-sight
depth of the emitting region.
So long as the emissivity fluctuations are weak
and uncorrelated with the velocity fluctuations, then \(n\DD = n\DDD\)
\citep{Miville-Deschenes:2003a, Levrier:2004a},
but if these conditions are not satisfied, then the structure function
of the velocity centroids does not purely reflect the velocity power spectrum
\citep{Brunt:2004a, Esquivel:2005a, Ossenkopf:2006a, Esquivel:2007b}
and one has \(m\DD = n\DDD - 2 + \delta\kappa\) where \(\delta\kappa\) is a correction factor
that accounts for the contribution to the structure function from
column density fluctuations and cross terms (see section \ref{sec:constancy-power-law}).

\citet{Brunt:2004a} found that \(\delta\kappa\) is a function of the Mach number for
hydrodynamic turbulent box simulations.  In principle,
we could calculate \(\delta\kappa\) for
the fractional Brownian motion models that we use here
by using the analytic machinery of \citet{Esquivel:2007b},
but we prefer instead to use a more empirical approach.
We vary \(n\DDD\) until the
resultant structure function slope matches a particular value in the
range \(m\DD = 0.8 \to 1.2\)
that encompasses our observational results.\footnote{%
  Note that \(m\DD\) is written simply as \(m\) in the main text.
}
At each step, we estimate \(m\DD\) by fitting our idealized model structure function
(equation~\eqref{eq:model-strucfunc-ideal}, without the seeing and noise terms)
to the structure function of the simulated velocity map.
In the case of a uniform emissivity field (\(\shortsig{E} = 0\)),
we find \(\delta\kappa \approx 0\),
which is maximal projection smoothing, exactly as expected for a case that
mimics incompressible turbulence (see Appendix of \citealt{Miville-Deschenes:2003a}).
As the amplitude of the emissivity fluctuations increase,
we find that \(\delta\kappa\) becomes increasingly negative,
with \(\delta\kappa \approx -0.3\) for \(\shortsig{E} = 1\) (the case that we illustrate here)
and \(\delta\kappa \approx -0.55\) for \(\shortsig{E} = 2\).
This is qualitatively consistent with the results in
Figure~12a of \citet{Brunt:2004a}, although a quantitative
comparison is hard to make, since they are not holding \(m\) constant
in the way we do here. 
\stopNEW
